Minimizing post-shock forecasting error using disparate information

### 2020-08-25 manuscript/manuscript.tex
revisions to comments; see major revision in the last paragraph of discussion and model setup

% use packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{url}
\usepackage{authblk}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{caption}
\usepackage{float}
\usepackage[caption = false]{subfig}
\usepackage{tikz}
\usepackage{multirow}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
% margin setup
\geometry{margin=0.8in}

@@

In our methodological framework, the researcher creates a synthetic panel of disparate time series which have undergone similar structural shocks in the past. Construction of the donor pool that forms this synthetic panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}. As in SCM, care is needed when forming the donor pool of disparate time series. However, there are key differences between our framework and SCM. We assume that the disparate time series are independent from the time series under study before the timing of the shock. We also assume that the shock effects for each disparate time series are independent realizations from some unknown distribution with existing first and second moments.

@@

In this article, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random-effect structure. Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical}. In our model, the donor pool can consist of dependent time series but time series within the donor pool should be independent of the time series of interest. However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method. 
%The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point. 
We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. Our auto regressive model will consider present day covariates to better motivate similarity weighting. The considered adjustment strategies all target the mean of the shock effect distribution. Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop. We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design. We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020. We will show that our proposed adjustment estimators yield much better results than no adjustment in this setting. We also use this example to demonstrate settings in which the shock effect may be decomposed into separate estimable parts. We now motivate our framework for post-shock forecasting.

@@

Let $I(\cdot)$ be an indicator function, $T_i$ be the time length of the time series $i$ for $i = 1, \ldots, n+1$, and $T_i^*$ be the time point just before the one when the shock is known to occur, with $T_i^* < T_i$.  For $t= 1, \ldots, T_i$ and $i = 1, \ldots, n+1$, the model $\mc{M}_1$ is defined as
\begin{align}
\mc{M}_1 \colon y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\label{equation1}
\end{align}
 where $D_{i,t} = I(t = T_i^* + 1)$ 
and $\x_{i,t} \in \R^{p}$ with $p \geq 1$.  We assume that the 
$\mbf{x}_{i,t}$'s are fixed. Let $|x|$ denote the absolute value of $x$ for $x\in \reals$. For $i = 1, \ldots, n+1$ and $t=1, \ldots, T_i$, the random effects structure for $\mc{M}_1$ is:
\begin{align*}
  \eta_i &\simiid  \; \E{\eta_i} = 0, \var{\eta_i} = \sigma^2_{\eta}\\
  \phi_i &\simiid \; |\phi_i|<1, \\
   \theta_i &\simiid  \; \E{\theta_i}=\mu_{\theta}, \var{\theta_i}=\Sigma_{\theta}^2 \\
\alpha_i &\simiid \; \E{\alpha_i}=\mu_{\alpha}, \var{\alpha_i}=\sigma_{\alpha}^2, \\
\varepsilon_{i,t} &\simiid \; \E{\varepsilon_{i,t}} =0, \var{\varepsilon_{i,t}}=\sigma^2 \where \sigma > 0 ,  \\
\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t}.
\end{align*}
Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
for $i = 1, \ldots, n+1$.  %Although synthesizing information from disparate time series assumes similarities of shock effects, shock effects may differ in terms of their means in practice. 
We also consider a model where the shock effects are linear functions of covariates with an additional additive mean-zero error.
%Additionally, $\mc{M}_1$ can be further improved in the sense that the shock effects may depend on the covariates around the shock time points, i.e., $T_i^*$ for $i = 1, \ldots, n+1$. 
%$\mc{M}_2$ can be constructed to accommodate those issues by imposing additional structures on the means of $\alpha_i$ as in (\ref{model2}) for $i = 1, \ldots, n+1$.
For $i = 1, \ldots, n+1$, the random effects structure for this model (model $\mc{M}_2$) is:
\begin{align}
\mc{M}_2 \colon \begin{array}{l}
  y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+ \t{\varepsilon}_{i},
\end{array}\label{model2}
\end{align}
 where the added random effects are
\begin{align*}
\t{\varepsilon}_{i} &\simiid  \E{\t{\varepsilon}}=0, \var{\t{\varepsilon}}=\sigma^2_{\alpha} \where \sigma_{\alpha}>0\\
\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
\end{align*} 
We further define 
$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}$. 
We will investigate the post-shock aggregated estimators in $\mc{M}_2$ 
in settings where $\delta_i$ is either fixed or random. 
We let $\mc{M}_{21}$ denote model $\mc{M}_{2}$ with $\delta_i = \delta$ for $i= 1, \ldots, n+1$, 
where $\delta$ is a  fixed unknown parameter.
We let $\mc{M}_{22}$ denote model $\mc{M}_{2}$ with the following random effects 
structure for $\delta_i$:
\begin{align*}
\delta_i \overset{iid}{\sim}\;  \mrm{E}(\delta) = \mu_\delta, \var{\delta} = \Sigma_\delta
   \quad \text{ with } \quad  \delta_i  \indep \t{\varepsilon}_{i}.
\end{align*}
We further define the parameter sets
\begin{align}
  \begin{array}{lll}
     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}
  \end{array}
\end{align}
where $\Theta$ and $\Theta_1$ can adapt to $\mc{M}_1$ by dropping $\delta_i$. We assume this for notational simplicity.

@@

We now construct the aggregated estimators of the shock effects that appear in 
Forecast 2 (see Section \ref{forecast}). We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.  %Notice that the shock effect 
%for time series $1$ is typically unobserved. But we can gather knowledge from 
%disparate time series to construct some sort of estimators that may be helpful for 
%estimating $\E{\alpha_1}$. 
First, we introduce the procedures of parameter estimation for 
$\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}). 
Conditional on all regression parameters, previous responses, and covariates, 
the response variable $y_{i,t}$ in $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ 
has distribution 
$$
  y_{i,t} 
    \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i'\x_{i,t} 
      , \sigma^2).
$$
For $i = 2, \ldots, n+1$, all parameters in this model will be estimated with ordinary least squares 
(OLS) using historical data of $t = 1, \ldots, T_i$. For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$. In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate 
of $\alpha_i$.  Note that parameter estimation 
for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.  We emphasize that $\alpha_i$s are random variables but the OLS estimation is conditioned on the their realizations from some distribution.

@@

\begin{remark}
% Though in Section \ref{modelsetup} we assume $\mbf{x}_{i,t}\in \reals^p$ and bases construction for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$  on this fact, we will shortly show that the covariates need not be of the same dimension across disparate time series. 
In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta_i \in \reals^p$. 
 % We can insert $\mathbf{0}$ into the covariates of disparate time series for the parts that they do not share. For example, suppose $\mathbf{x}_{2, t}, \mathbf{x}_{2, t-1}\in \reals^{p-1}$ and $\mathbf{x}_{3, t}, \mathbf{x}_{3, t-1}\in \reals^p$ are the covariates for time series 2 and 3. Assume that the $p$th column of $\mathbf{x}_{3, t}, \mathbf{x}_{3, t-1}$ is the part they do not share. In this case, we can let $\mathbf{x}^{adj}_{2, t}=(\mathbf{x}_{2, t}, \mathbf{0})$, $\mathbf{x}^{adj}_{2, t-1}=(\mathbf{x}_{2, t-1}, \mathbf{0})$ to satisfy the $p$-dimension requirement. 
However, it is not necessary that the all $p$ covariates are important for every time series under study. The regression coefficients $\theta_i$ are nuisance parameters that are not of primary importance. 
% In this regard, OLS estimations in software can reparameterize the design matrix.  Of course, the column space of the design matrix does not change compared to the one in original dimension. Thus, the least squares estimators do not change. In other words, OLS estimation need no adjustment. The generalization may only apply to the construction of weighted-adjustment  estimator $\hat{\alpha}_{\rm wadj}$.
It will be understood that structural 0s in $\theta_i$ correspond to variables that are unimportant. 
\end{remark}

@@

\begin{enumerate}[label = (\roman*)]
  \item Under $\mc{M}_1$ and $\mc{M}_{21}$,  
\begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
\end{align*}
\item Under $\mc{M}_{22}$, 
\begin{align*}
\var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
\end{align*}
\end{enumerate}
Formal justification for these results can be found in Appendix. Note that the variances are not comparable in closed-form %we shall see that it is difficult to compare variances between $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ 
because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our auto regressive model formulation.

@@

In the first simulation setup, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$. Note that $\E{\E{\alpha_1}}=52$, where the last expectation is operated under the density of the covariates. In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost. Results are displayed in Table~\ref{table1}.

In the second simulation setup, we consider the parameter combination of $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $n=10$. Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$. Results are  in Table~\ref{table2}.

>>>>

% use packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{url}
\usepackage{authblk}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{caption}
\usepackage{float}
\usepackage[caption = false]{subfig}
\usepackage{tikz}
\usepackage{multirow}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
\usepackage{pdflscape}
% margin setup
\geometry{margin=0.8in}

@@

In our methodological framework, the researcher creates a synthetic panel of disparate time series which have undergone similar structural shocks in the past. Construction of the donor pool that forms this synthetic panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}. As in SCM, care is needed when forming the donor pool of disparate time series. However, there are key differences between our framework and SCM. We assume that the disparate time series are independent from the time series under study before the timing of the shock. Moreover, the shocks from candidate time series in the donor pool, together with the shock in the time series of interest, are assumed to be  from a common family of distributions with existing first and second moments.

@@

In this article, we will assume a simple autoregressive data generating process similar to that in \citet{blundell1998initial} with a general random-effect structure. Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical}. In our model, the donor pool can consist of dependent time series but time series within the donor pool should be independent of the time series of interest. However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method. 
%The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point. 
 We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. Our autoregressive model will consider present day covariates to better motivate similarity weighting. The considered adjustment strategies all target the mean of the shock effect distribution. Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop. We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design. We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020. We will show that our proposed adjustment estimators yield much better results than no adjustment in this setting. We also use this example to demonstrate settings in which the shock effect may be decomposed into separate estimable parts. We now motivate our framework for post-shock forecasting.

@@

Let $I(\cdot)$ be an indicator function, $T_i$ be the time length of the time series $i$ for $i = 1, \ldots, n+1$, and $T_i^*$ be the time point just before the one when the shock is known to occur, with $T_i^* < T_i$.  For $t= 1, \ldots, T_i$ and $i = 1, \ldots, n+1$, the model $\mc{M}_1$ is defined as
\mc{M}_1 \colon y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\label{equation1}
 where $D_{i,t} = I(t = T_i^* + 1)$ 
and $\x_{i,t} \in \R^{p}$ with $p \geq 1$.  We assume that the 
$\mbf{x}_{i,t}$'s are fixed. Let $|x|$ denote the absolute value of $x$ for $x\in \reals$. For $i = 1, \ldots, n+1$ and $t=1, \ldots, T_i$, the random effects structure for $\mc{M}_1$ is:
  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}\\
  \phi_i &\simiid \mrm{Uniform}(-1,1), \\
   \theta_i &\simiid \mc{F}_{\theta} \text{ with }  \; \mrm{E}_{\mc{F}_{\theta}}(\theta_i) = \mu_{\theta}, \mrm{Var}_{\mc{F}_{\theta}}(\theta_i)  = \Sigma^2_{\theta} \\
\alpha_i &\simiid \mc{F}_{\alpha} \text{ with }  \; \mrm{E}_{\mc{F}_{\alpha}}(\alpha_i) = \mu_{\alpha}, \mrm{Var}_{\mc{F}_{\alpha}}(\alpha_i)  = \sigma^2_{\alpha}  \\
\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t})  = \sigma^2 \where \sigma > 0 ,  \\
\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t}.
Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
for $i = 1, \ldots, n+1$.  %Although synthesizing information from disparate time series assumes similarities of shock effects, shock effects may differ in terms of their means in practice. 
We also consider a model where the shock effects are linear functions of covariates with an additional additive mean-zero error.
%Additionally, $\mc{M}_1$ can be further improved in the sense that the shock effects may depend on the covariates around the shock time points, i.e., $T_i^*$ for $i = 1, \ldots, n+1$. 
%$\mc{M}_2$ can be constructed to accommodate those issues by imposing additional structures on the means of $\alpha_i$ as in (\ref{model2}) for $i = 1, \ldots, n+1$.
For $i = 1, \ldots, n+1$, the random effects structure for this model (model $\mc{M}_2$) is:
\mc{M}_2 \colon \begin{array}{l}
  y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+ \t{\varepsilon}_{i},
\end{array}\label{model2}
 where the added random effects are
\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha} \where \sigma_{\alpha}>0\\
\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}$. 
We will investigate the post-shock aggregated estimators in $\mc{M}_2$ 
in settings where $\delta_i$ is either fixed or random. 
We let $\mc{M}_{21}$ denote model $\mc{M}_{2}$ with $\delta_i = \delta$ for $i= 1, \ldots, n+1$, 
where $\delta$ is a  fixed unknown parameter.
We let $\mc{M}_{22}$ denote model $\mc{M}_{2}$ with the following random effects 
structure for $\delta_i$:
\delta_i\simiid  \mc{F}_{\delta} \text{ with }\mrm{E}_{\mc{F}_{\delta}}(\delta_i)=\mu_{\delta}, \mrm{Var}_{\mc{F}_{\delta}}(\delta_i)=\Sigma_\delta 
   \quad \text{ with } \quad  \delta_i  \indep \t{\varepsilon}_{i}.
We further define the parameter sets
  \begin{array}{lll}
     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}
  \end{array}
where $\Theta$ and $\Theta_1$ can adapt to $\mc{M}_1$ by dropping $\delta_i$. We assume this for notational simplicity.

@@

We now construct the aggregated estimators of the shock effects that appear in 
Forecast 2 (see Section \ref{forecast}). We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.  %Notice that the shock effect 
%for time series $1$ is typically unobserved. But we can gather knowledge from 
%disparate time series to construct some sort of estimators that may be helpful for 
%estimating $\E{\alpha_1}$. 
First, we introduce the procedures of parameter estimation for 
$\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}). 
For $i = 2, \ldots, n+1$, all parameters in this model will be estimated with ordinary least squares 
(OLS) using historical data of $t = 1, \ldots, T_i$. For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$. In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate 
of $\alpha_i$.  Note that parameter estimation 
for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.  We emphasize that $\alpha_i$s are random variables but the OLS estimation is conditioned on the their realizations from some distribution.

@@

\begin{remark}
% Though in Section \ref{modelsetup} we assume $\mbf{x}_{i,t}\in \reals^p$ and bases construction for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$  on this fact, we will shortly show that the covariates need not be of the same dimension across disparate time series. 
\label{remark1}In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta_i \in \reals^p$. 
 % We can insert $\mathbf{0}$ into the covariates of disparate time series for the parts that they do not share. For example, suppose $\mathbf{x}_{2, t}, \mathbf{x}_{2, t-1}\in \reals^{p-1}$ and $\mathbf{x}_{3, t}, \mathbf{x}_{3, t-1}\in \reals^p$ are the covariates for time series 2 and 3. Assume that the $p$th column of $\mathbf{x}_{3, t}, \mathbf{x}_{3, t-1}$ is the part they do not share. In this case, we can let $\mathbf{x}^{adj}_{2, t}=(\mathbf{x}_{2, t}, \mathbf{0})$, $\mathbf{x}^{adj}_{2, t-1}=(\mathbf{x}_{2, t-1}, \mathbf{0})$ to satisfy the $p$-dimension requirement. 
However, it is not necessary that the all $p$ covariates are important for every time series under study. The regression coefficients $\theta_i$ are nuisance parameters that are not of primary importance. 
% In this regard, OLS estimations in software can reparameterize the design matrix.  Of course, the column space of the design matrix does not change compared to the one in original dimension. Thus, the least squares estimators do not change. In other words, OLS estimation need no adjustment. The generalization may only apply to the construction of weighted-adjustment  estimator $\hat{\alpha}_{\rm wadj}$.
It will be understood that structural 0s in $\theta_i$ correspond to variables that are unimportant. 
\end{remark}

@@

\begin{enumerate}[label = (\roman*)]
  \item Under $\mc{M}_1$ and $\mc{M}_{21}$,  
\begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
\end{align*}
\item Under $\mc{M}_{22}$, 
\begin{align*}
\var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
\end{align*}
\end{enumerate}
Formal justification for these results can be found in Appendix. Note that the variances are not comparable in closed-form %we shall see that it is difficult to compare variances between $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ 
because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.

@@

In the first simulation setup, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$. Note that $\E{\E{\alpha_1}}=52$, where the last expectation is operated under the density of the covariates. In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost. Results are displayed in Table~\ref{table1} in the Appendix \ref{tablesappendix}.

In the second simulation setup, we consider the parameter combination of $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $n=10$. Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$. Results are  in Table~\ref{table2} in the Appendix \ref{tablesappendix}.
